Wildcard: End user modification of web applications through a data table

### 2019-12-29 paper.tex
lotsa changes

In 2012, the travel site Airbnb removed the ability to sort listings by
price. Users could still filter down to a price range, but could no
longer view the cheapest listings first. Many users complained on online
message boards that the change seemed hostile to users---``It's so
frustrating!..What is the logic behind not having this function?'' says
one user on the
\href{https://community.withairbnb.com/t5/Hosting/Sorting-listing-by-price/td-p/559404}{Airbnb
support forum}. Alas, the feature remains missing to this day.

This is a familiar situation in a world of web applications that are
frequently updated without user consent. When web software doesn't quite
meet users' needs, their only recourse is to complain to the developers
and hope someone listens. Sometimes there is a way to use a browser
extension or user script to fix the issue, but making an extension
requires sophisticated programming skills. We see this as a waste of the
pliability of software and the openness of the Web. If users could make
tweaks to web applications without programming, a vast number of people
would gain the agency to modify software to meet their unique
preferences.

@@

In Wildcard, sorting Airbnb listings by price takes just one click on a
table header, with no programming required by the end user. Beyond
sorting and filtering data, Wildcard also supports a broad set of other
use cases like accessing third party APIs, performing small
computations, recording private user annotations to the page, and using
alternate UI widgets to enter data.

Wildcard currently requires a programmer to manually define an adapter
between the original page and the data table using web scraping
techniques. Even though programming is still required for part of the
process, this forms an effective collaboration between the programmer
and the end user, since the end user is able to perform a wide variety
of modifications to a site once a single adapter is defined. Eventually,
we envision adapter creation being less of a burden by making it
automated or making it possible for end users to build adapters.

@@

Let's see an example of how an end user might modify a website with
Wildcard in practice.

>>>>

In 2012, the travel site Airbnb removed the ability to sort listings by
price. Users could still filter down to a price range, but could no
longer view the cheapest listings first. Many users complained on online
message boards that the change seemed hostile to users. ``It's so
frustrating!..What is the logic behind not having this function?'' says
one user on the
\href{https://community.withairbnb.com/t5/Hosting/Sorting-listing-by-price/td-p/559404}{Airbnb
support forum}. Alas, the feature remains missing to this day.

This is a familiar situation in a world of web applications that are
frequently updated without user consent. When web software doesn't quite
meet users' needs, their only recourse is to complain to the developers
and hope someone listens. Sometimes there is a way to use a browser
extension or user script to fix the issue, but making an extension
requires sophisticated programming skills. We see this as a waste of the
openness of the Web platform, and of the pliability of software in
general. If users could make tweaks to web applications without
programming, a vast number of people would gain the agency to modify
software to meet their unique preferences.

@@

In Wildcard, sorting Airbnb listings by price takes just one click on a
table header, with no programming required by the end user. Beyond
sorting and filtering data, Wildcard also supports a variety of other
use cases like accessing third party APIs, performing small
computations, recording private user annotations, and using alternate UI
widgets. While Wildcard does not support all changes someone might want
to make to a website, the goal of the project is to make a broad subset
of changes easily accessible to end users.

Under the hood, there is no magic---Wildcard currently requires a
programmer to manually define an adapter between the original page and
the data table using web scraping techniques. While programming is
required for part of the process, this forms a useful collaboration
between the programmer and the end user, since the end user is able to
perform many different modifications once an adapter is defined. We also
plan to eventually reduce the burden of making adapters (discussed in
more detail later).

@@

To get a sense of the user experience of Wildcard, let's see an example
of how an end user can modify a website with Wildcard in practice.
